Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-08-26 paper/tex/analysis.tex
few more words on individual PDFs

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we will dedicate some attention to breaking it apart.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from the true \pz\ likelihoods, which is not how most existing datasets have been constructed.  Instead, data is often taken from actual observations, or generated from mock catalogs derived from N-body simulations of the Universe (as is the case in this study).  In these cases there is no ``true PDF'' for an individual object, and most measures of PDF fidelity will need to rely on ensemble properties of the similar objects, or the entire sample.  We mention a potential project addressing this issue in \S\,\ref{sec:futureexperiments}.
%a mock catalogue generation procedure that has not yet appeared in the literature and was not performed for this work.

@@

\subsection{Metrics of \pzpdf ensembles}
\label{sec:qualmet}
%(Rongpu Zhou, Jeffrey Newman, Alex Malz)
%(Alex Malz, Peter Freeman, Sam Schmidt)
%(John Soo, Rongpu Zhou)

>>>>

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we will dedicate some attention to breaking it apart.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from the true \pz\ likelihoods, which is not how most existing datasets have been constructed.  Instead, data is often taken from empirical observations, or generated from mock catalogs derived from N-body simulations of the Universe (as is the case in this study).  In these cases there is no ``true PDF'' for an individual object given its observed properties, as for real data the true redshift distribution is unkown, and for simulations the photometric data is usually generated by empirical or semi-analytic relations tied to the underlying dark matter distribution and local environment.  As a consequence, most measures of PDF fidelity will need to rely on ensemble properties of the similar objects, or the entire sample.  We do discuss a metric that can measure performance of individual PDF quality, the conditional density estimate loss, in \S\,\ref{sec:CDE_loss}.  We also mention a potential future project addressing this issue in \S\,\ref{sec:futureexperiments}.
%a mock catalogue generation procedure that has not yet appeared in the literature and was not performed for this work.

@@

\subsection{Metrics of \pzpdf \ ensembles}
\label{sec:qualmet}
%(Rongpu Zhou, Jeffrey Newman, Alex Malz)
%(Alex Malz, Peter Freeman, Sam Schmidt)
%(John Soo, Rongpu Zhou)

### 2019-08-26 paper/tex/discussion.tex
few more words on individual PDFs

Furthermore, our metrics are not necessarily able to assess the fidelity of individual \pzpdf s relative to true posteriors.
Metric-specific performance implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.

>>>>

Furthermore, our metrics are not necessarily able to assess the fidelity of individual \pzpdf s relative to true posteriors: in the absence of a ``true PDF'' from which redshifts are drawn, it is difficult to construct metrics to measure performance for individual galaxies rather than ensembles, with the exception of the CDE Loss metric of section~\ref{sec:CDE_loss}, where knowledge of the true densities is not required in computing the Loss function for an individual galaxy.  A lack of appropriate metrics more sophisticated than the CDE Loss remains an open issue for science cases requiring accurate individual galaxy PDFs.
The metric-specific performance demonstrated in this paper implies that we may need multiple \pzpdf\ approaches tuned to each metric in order to maximize returns over all science cases in large upcoming surveys.
